
\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{#1}}
%\rhead{\tiny\itshape\leftmark{}}
\lhead{\scriptsize\itshape\medskip Bibliography}
\chead{} \rfoot{\scriptsize\medskip\itshape Anil Chindhe}
%\cfoot{\medskip\sffamily\large\thepage }
\lfoot{\scriptsize\medskip\itshape Balbhim College,Beed.}
\renewcommand{\headrulewidth}{0.01pt}
\renewcommand{\footrulewidth}{0.01pt}
%\def\baselinestretch{1}

%\begin{small}
\begin{thebibliography}{00}
\lhead{\scriptsize\itshape\medskip References}
%%%A

\bibitem{R1} {\sl Adomian G.;}{\it Solving Frontier Problems of Physics: The Decomposition Method,}Kluwer Academic Publishers. Boston. MA. (1994).

\bibitem{R2}{\sl Adomian G.A.;} Review of the Decomposition Method in Applied Mathematics, {\it J. Math. Anal.Appl.,}{\bf 135},501-–544,(1988).


\bibitem{R3} {\sl Agrawal N.K.;}Study of certain Integral Transforms of Generalized Functions,{\it Ph.D. Thesis, Ranchi University},(1977).

\bibitem{R4}{\sl Apostol T. M.;}{\it Mathematical analysis},2nd ed.,Addison-Wesley Publishing
Co.World Student Series edition,(1974).

\bibitem{R5}{\sl Asiru M. A.;} Sumudu transform and solution of integral equations of convolution type ,{\it Internat. J. Math. Ed. Sci. Tech.,}{\bf 32}, 906--910,(2011).

\bibitem{R6} {\sl Asiru M. A .;}Further Properties of the Sumudu Transform and its Applications, {\it Inter. J. Math. Ed. Sci. Tech.,}{\bf 33(2)},441-–449, (2002).

\bibitem{R7} {\sl Asiru M. A.;} Applications of the Sumudu Transform to Discrete Dynamic system ,
{\it Inter. J. Math. Ed. Sci. Tech.,} {\bf 34(6)},944–-949, (2003).

\bibitem{R8}{\sl Assine Benia, Boubaker-Khaled Sadallah;}Existence of Solutions to Burgers Equations in Domains That can be Transformed into Rectangles.{\it Electronic Journal of Differential Equations,}{\bf 157},1--13,(2016)

\bibitem{R9} {\sl Baile J.E.,Ollis D.F.;}  {\it Biochemical Engineering Fundamentals,}McGraw-Hill,Inc.Second Edition,Singapore, (1986).

 
\bibitem{R10}{\sl Belgacem F.B.M.,Karaballi A.A.,Kalla L. S.;}Analytical investigations of
the Sumudu transform and applications to integral production equations,{\it Math.Probl. Eng.,}{\bf 3(4)},103--118,(2003).

\bibitem{R11}{\sl Belgacem F.B.M.,Karaballi A.A.;} Sumudu transform fundamental properties investigations and applications,{\it Journal of Applied Mathematics and Stochastic Analysis,}{\bf 3(4)},1–-23,(2006).

\bibitem{R12}{\sl Belgacem F.B.M.,Silambarasan R.;}Applications of the Natural transform to Maxwell's Equations,{\it PIERS Suzhou,China,} 899--902,(2011).

\bibitem{R13}{\sl Belgacem F.B.M.,Silambarasan R.;}Theory of the Natural transform,{\it Mathematics in Engineering Science and Aerospace(MESA)journal,}{\bf 3(1)},99--124,(2012).

\bibitem{R14}{\sl Belgacem F.B.M.,Silambarasan R.;} Advances in the Natural transform,{\it 9th International Conference on Mathematical Problems in Engineering.Aerospace and Sciences AIP Conference Proceeding,}{\bf 1493},106-110,(2012).

\bibitem{R15}{\sl Belgacem F.B.M.;}Boundary Value Problem with Indefinite Weight and Applications,
{\it International Journal of Problems of Nonlinear Analysis in Engineering Systems,}
{\bf 10(2)}, 51--581, (1999).

\bibitem{R16}{\sl Belgacem F.B.M.;}Applications of the Sumudu Transformation Indefinite Periodic Parabolic Equations, {\it Proceedings of the International Conference on Nonlinear Problems and Aerospace Applications, Budapest, Hungary,} 1–-10, (2007).

\bibitem{R17}{\sl Belgacem F.B.M.;}Introducing and Analysing Deeper Sumudu Properties ,{\it Nonlinear Studies Journal,} {\bf 13(1)}, 23–-41,(2006).


\bibitem{R18}{\sl Bhosale B.R.More,S.V.;} The Complex Mellin-Hankel transformation of generalized functions, {\it Vijnan Shodh Bharti,} {\bf l},1--14 (1978).

\bibitem{R19}{\sl Bhonsle B.R.,Chaudhary M.S.;} The complex Laplace-Hankel transformation of generalized functions, {\it Indian J. Pure. Appl.Math.,} {\bf 7(2)},205--211,(1976).

\bibitem{R20}{\sl Bhonsle B.R.;} On some results involving Generalized Laplace transforms,{\it Bull. Cal. Math. Soc.,} {\bf 5(1)},(1956).

\bibitem{R21}{\sl Bhonsle B.R.;}On a property of Generalized Laplace transform,{\it Bull. Cal.Math. Soc.,}{\bf 50(1)},6--8,(1958).

\bibitem{R22}{\sl Burgers J.M.;}A mathematical model illustrating the theory of turbulence,{\it Advances in Applied Mechanics,}{\bf 1},171--199,(1948).

\bibitem{R23}{\sl Chaudhary M.S.;} Topological and Distributional aspects of Laplace-Hankel transformation and its applications, {\it Ph.D. thesis,Marathwada University},(1974).

\bibitem{R24}{\sl Chindhe A.D.,Kiwne S.B.;}Application of Combine Natural Transform and Adomian Decomposition Method in Volterra Integro-Differential Equations,{\it Mathematical Journal of Interdisciplinary Sciences,}{\bf 5(1)},1–-14,(2016).

\bibitem{R25}{\sl Chindhe A.D.,Kiwne S.B.;}Natural Transform and Special Functions,{\it Journal of New Theory,}{\bf 15},39--47,(2017). 

\bibitem{R26}{\sl Cheng J.-F.,Chu Y.-M.;} Solution to the linear fractional differential equation using Adomian decomposition method, {\it Mathematical Problems in Engineering} ; Article ID 587068,14 pages,(2011).

\bibitem{R27}{\sl Cherruault Y,Adomian G.;} Decomposition method: a new proof of convergence,{\it Math Comput Modell,}{\bf 8},103–106,(1993).

\bibitem{R28}{\sl Cherrualt Y,Saccamandi G;}Some  New results for convergence of Adomian's method applied to integral equations,{\it Math
Comput Modell},{\bf16},83-–93,(1992).


\bibitem{R29}{\sl Copper J.L.B.;} Laplace transformation of distributions, {\it Canadian J. Math.,}{\bf 18},1325--1332,(1966).

\bibitem{R30}{\sl Deshna Looner,P.K.Banerji;}Natural transform for distribution and Boehmian space,{\it Mathematics in Engineering ,Science and Aerospace MESA,}{\bf 4(1)},69--76,(2013).

\bibitem{R31}{\sl Deshna Looner,P.K.Banerji;}Application of Natural transform to differential equations,Journal Indian Academy of Mathematics.35(1),151-158,(2013).

\bibitem{R32}{\sl Deshna Looner,P.K.Banerji;}On the solution of distributional Abel integral equation by distributional Sumudu transform, Internat. J. Math. Math. Sci. 2011 , 1-8, Article ID 480528,(2011).

\bibitem{R33}{\sl Deshna Looner,P.K.Banerji;}Fractional Integrals and Derivatives for Sumudu transform on distribution spaces,Appl. Appl. Math. Internat. J. 7 (1) , 188-200,(2012).

\bibitem{R34}{\sl Deshna Looner,P.K.Banerji, Debnath, Lokenath;} Hartley Transform for Integrable Boehmians, {\it Int.Trans. Spl.Funct.,} {\bf 21 (6)},459--464,(2010).


\bibitem{R35}{\sl Dijksma R.V.,Desnoo H.S.V. ;}Distributional Watson transforms,{\it SIAM J.Math.Anal.,}{\bf 5},888--892,(1974).

\bibitem{R36}{\sl Dirac P.A.M.;} {\it The principles of quantum mechanics},Calrendon Press,Ox-ford, (1947).

\bibitem{R37}{\sl Edwards R.E.;} {\it Functional Analysis},Holt,Hinehart and Winston,New York, (1965).

\bibitem{R38}{\sl Gelfand I.M.,Shilov G.E.;}{\it Generalized Functions} Vol.III, Academic Press, NY, (1967).

\bibitem{R39}{\sl Gelfand I.M.,Shilov G.E.;}{\it Generalized Functions} Vol.I, Academic Press,NY, (1964).

\bibitem{R40}{\sl Gupta, R.K.,Gupta S.C.;}Unsteady flow of a dusty gas in cylinders with circular and sectorial cross section,{\it Proc. Indian acad. Sci.,}{\bf 86A(6)},591--601,(1977).


\bibitem{R41}{\sl Gupta, R.K.,Gupta S.C.;}Some operational properties of generalized Legendre transform and their applications,{\it
Indian J.Pure appl.Math,}{\bf 5},589--601,(1977).

\bibitem{R42} {\sl Hassan Eltayeb ,Adem Kilicman ,Brian Fisher;}New integral transform and associated distributions,{\it Integral Transforms and Special functions,}{\bf 21},367--379,(2010).

\bibitem{R43}{\sl Hassan Eltayeb and Adem Kilicman ;}Application of Sumudu Decomposition Method to Solve Nonlinear System Volterra Integro-differential Equations,{\it Abstract and Applied Analysis}{\bf Volume 2014}, Article ID 503141, 6 pages,(2014).

\bibitem{R44}{\sl Hassan Eltayeb and Adem Kilicman ;}Application of Sumudu Decomposition
Method to Solve Nonlinear System of Partial
Differential Equations,{\it Abstract and Applied Analysis,} {\bf vol. 2010}, Article ID 598702, 11 pages, (2010).

\bibitem{R45}  Hassan Eltayeb and Adem Kilicman \textit{Application of Sumudu Decomposition
Method to Solve Nonlinear System of Partial
Differential Equations} ,Abstract and Applied Analysis, vol. 2010, Article ID 598702, 11 pages, 2010.

\bibitem{R46} {\sl Hassan Eltayeb and Adem Kilicman;}Application of Sumudu Decomposition Method to Solve Nonlinear System Volterra Integro-differential Equations,{\it Abstract and Applied Analysis}{\bf 2014}, Article ID 503141, 6 pages

\bibitem{R47} {\sl He J.-H.} Homotopy perturbation technique,{\it Computer Methods in Applied Mechanics and Engineering ,}{\bf 178(3-4)} , 257–-262,(1999).

\bibitem{R48} {\sl Jagdev Singh, Devendra Kumar, and A. Kilicman;} Homotopy Perturbation Method for Fractional Gas Dynamics Equation Using Sumudu Transform,{\it Abstract and Applied Analysis }{\bf  2013}, Article ID 934060, 8 pages


\bibitem{R49}{\sl Jones D.S.;}{\it Generalized functions},McGraw-Hill, NY,(1966).

\bibitem{R50}{\sl Kamal Shah, Muhammad Junaid, Nigar Ali.;}Extraction of Laplace,Sumudu,Fourier
and Mellin Transform from the Natural Transform,{\it J. Appl. Environ. Biol. Sci.,}{\bf 5(9)},108–-115, (2015).

\bibitem{R51}{\sl Khan Z.H.,Khan W.A.;}N-transform properties and applications,{\it NUST Journal of Engineering Sciences,}{\bf 1(1)},127--133,(2008).


\bibitem{R52}{\sl Kılıcman A., Eltayeb H.;}A Note on Classification of Hyperbolic and Elliptic
Equations with Polynomial Coefficients,{\it Applied Mathematics Letters},{\bf 21(11)}, 1124-–1128, (2008).

\bibitem{R53}{\sl Korevaar, J.;}Distributions defined from the point of view of applied mathematics, {\it K. Ned. Akad. Wetenschap, Ser.A,}{\bf 58},368--389,483--503,663--674,(1955).


\bibitem{R54}{\sl Liverman, T.P.G.;}{\it Generalized functions and direct operational methods} Vol-1, Prentice Hall, Englewood Cliffs, NJ,(1964).

\bibitem{R55}{\sl Malgonde, S.P., Saxena, R.K.;} Generalized Meijer-Laplace transformation of generalized functions, {\it J. Proc. Nat. Acad. Sci.,}{\bf Sec.A, Part III}, 235--244,(1985).

\bibitem{R56}{\sl Misra, O.P.;}Some Abelian Theorems for Distributional Stieltjes Transformations,{\it J.Math.Anal.AppL,} {\bf 39(3)},590--599,(1972).

\bibitem{R57} {\sl Murray J.D.;}{\it Mathematical Biology},springer,berlin ,(1993).

\bibitem{R58}{\sl Orton, Marion ;} Hilbert transforms, Plemelj relations and Fourier transforms of distributions,{\it SIAM J.Math.Anal., }{\bf 4}, 656--670,(1973).

\bibitem{R59}  {\sl Pamuk S.;} The Decomposition Method For Continuous Population Model : Single and Interacting Species,{\it Appl.Mat Comput.,}{\bf 163},79--88, (2005).

\bibitem{R60} {\sl Pathak, R. S.;}{\it Integral Transforms of Generalized Functions and their Applications},Gordon and Breach Science Publishers,Australia, Canada, India, Japan (1997).

\bibitem{R61} {\sl Pathak, R.S.;}A distributional generalized Stieltjes transformation, {\it Proc.Edin.Math.Soc.,} {\bf 20},15--22,(1976).

\bibitem{R62}{\sl Rainville E.D.;} {\it Special Functions,} Macmillan, New York, (1960).


\bibitem{R63}{\sl Rao G.N.L.;}Study of certain distributional transforms,{\it Ph.D. Thesis,Ranchi University},(1972).

\bibitem{R64}{\sl Rao G.N.L.;}The n-dimensional generalized Laplace transformation of certain distributions, {\it J.Indian Math.Soc.,}{\bf 39},219--226,(1975).

\bibitem{R65}{\sl Reza Abazari, Borhanifar A.;}Numerical study of the solution of the Burgers and coupled Burgers equations by a differential transformation method,{\it Computers and Mathematics with Applications,}{\bf 59},2711--2722,(2010).

\bibitem{R66} {\sl Reddy, B.P.;}Some Contributions to the theory of distributional integral transforms,{\it Ph.D. thesis, Shivaji University, Kolhapur},(1993).

\bibitem{R67} {\sl Saksena, K.M.;}Inversion and representation theorems for a generalization of
Laplace transformation, {\it Pacific J. Math.,}{\bf 8(3)}, 597--607,(1958).

\bibitem{R68}{\sl Sadikali Latif Shaikh;}A Study of some Integral Transforms and their Operational Calculus,{\it Ph.D.Thesis,Shivaji University,Kolhapur,} (2011).

\bibitem{R69}{\sl Sadikali Latif Shaikh;}Some Abelian Theorems for the Classical Sumudu Transform,{\it American International Journal of
Research in Science, Technology,
Engineering and Mathematics,}{\bf 18(1)},95--97,(2017).


\bibitem{R70}{\sl Shiraishi Risai;} On the value of a distribution at a point and multiplicative products,{\it J. Sci. Hiroshima Univ. Ser. A-I,}{\bf 31 },89--104,(1967).

\bibitem{R71} {\sl Sobolev, S.L.;}Mehthode nouvelle a resoudre le probleme de Cauchy pourless equations lineaires hyperboliques normales, {\it Math. Sbornik,} {\bf 1}, 39--72,(1936).

\bibitem{R72} {\sl Schwartz, L.;}{\it Theorie des distributions} Vol.I, Hermann Press, (1957).

\bibitem{R73} {\sl Schwartz, L.;}{\it Theorie des distributions} Vol.II, Hermann Press, (1959).

\bibitem{R74} {\sl Sharma, S.D.,Gupta R.K. ;} Generalized finite Sine transform and
its applications, {\it Bull.Cal.Math.Soc.} {\bf 72} 125--133, (1980).

\bibitem{R75}{\sl S.K.Q.Al-Omari;}Hartley transforms on a certain space of generalized functions,{\it Georgian Mathematical Journal}{\bf 20(3)}, 415-426,(2013).

\bibitem{R76}{\sl S.K.Q.Al-Omari;}On the distributional Mellin transformation and its extension to Boehmian spaces,{\it Int. J. Contemp. Math. Sciences}{\bf 6 (17)}, 801--810,(2011).

\bibitem{R77}{\sl S.K.Q.Al-Omari;}The Generalized Steltjes and Fourier Transforms of Certain Spaces of Generalized Functions,{\it Deanship of Research and Graduate Studies}, Yarmouk University, Irbid, Jordan,(2009).

\bibitem{R78}{\sl S.K.Q.Al-Omari;}Generalized functions for double Sumudu transformation,{\it International Journal of Algebra,}{\bf 6 (3)}, 139--146,(2011).

\bibitem{R79}{\sl S.K.Q.Al-Omari;}Some Approch  to a  Generalized Hartley  Transform  Pair  in the Class of Generalized Function,{\it Far East Journal of Mathematical Sciences,} {\bf 101 (7)}, 1533-1545,(2017.)

\bibitem{R80}{\sl S.K.Q.Al-Omari;}On the Extended Fourier Transform of Generalized Functions,{\it Journal of Concrete and Applicable Mathematics} {\bf 13(3-4)}, 219--231,(2015).

\bibitem{R81}{\sl S.K.Q.Al-Omari;}On The Generalized Sumudu Transforms,{\it Journal of Applied Functional Analysis} {\bf 9},(2009).

\bibitem{R82}{\sl Tandale M.S. and Panchal S.K.;}On Laplace-Marchi-Zgrablich  Integral Transformation of Generalized Functions  and its Applications {\it Ph.D. Thesis,Dr.BabasahDeb Ambedkar Marathwada University,Aurangabad },(2013).

\bibitem{R83}{\sl Taghizadeh N,Akbari M,Ghelichzadeh A.;}Exact Solution of Burgers Equations by Homotopy Perturbation Method and Reduced Differential Transformation Method,{\it Australian Journal of Basic and Applied Sciences,}{\bf 5(5)},580--589,(2011).

\bibitem{R84}{\sl Thange T.G. and Chudhary M.S.;}Some Integral Transform on Distribution Spaces,{\it Ph. D. Thesis, Shivaji University}, Kolhapur, (2013).

\bibitem{R85}{\sl Tiwari, U.N.;}Some distributional transformations and Abelian theorems,{\it Ph.D.Thesis, Carleton University,} Ottawa, (1976).

\bibitem{R86}{\sl Ucer Y,Yagmurlu NM,Tasbozan O.;}Numerical Solutions of the Modified Burger's Equation by Finite Difference Methods,{\it Journal of Applied Mathematics Statistics and Informatics,}{\bf 13(1)},19--30,(2017)

\bibitem{R87}{\sl Varma, R.S.;}On a generalization of Laplace transform, {\it Proc. Nat. Acad. Sci.,
Sc.A,} {\bf 20}, 209--216,(1951).

\bibitem{R88}{\sl Treves F.;}{\it Topological Vector Spaces,Distributions and Kernels},Academic Press,New York,(1967).

\bibitem{R89}{\sl Watugala G. K.;}Sumudu transform: a new integral transform to solve differential equations and control engineering problems,{\it  Model Assisted Statistics and Applications}{\bf 24(1)},35-–43,(1993).

\bibitem{R90}{\sl  Watugala G. K.;}Sumudu Transform A New Integral Transform to solve Differential Equations and Control Engineering Problems, {\it Mathematical Engineering in Industry,} {\bf 6(4)}, 319–-329, (1998).

\bibitem{R91}{\sl Watugala G. K.;}The Sumudu transform for functions of two variables,{\it Mathematical Engineering in Industry,} {\bf 8(4)}, 293–-302, (2002).

\bibitem{R92}{\sl Wazwaz A.M.;} The combined Laplace transform–Adomian decomposition method
for handling nonlinear Volterra integro–differential equations,{\it Applied Mathematics and Computation,}{\bf 216},1304–-1309,(2010).

\bibitem{R93}{\sl Wazwaz A.M.;} A new algorithm for calculating Adomian polynomials for nonlinear operators,{\it Appl Math Comput,} {\bf 111},33–
-51,(2001).

\bibitem{R94}{\sl Wazwaz A.M.;}{\it Partial Differential Equations:Methods and Applications,}Balkema,Leiden,(2002).
 

\bibitem{R95}{\sl Weerakoon S.;}Applications of Sumudu Transform to Partial Differential
Equations,{\it Int. J. Math. Educ. Sci. Tech.} {\bf 25(2)},277–-283,(1994).
 
\bibitem{R96} {\sl Weerakoon S.;}Complex Inversion formula for Sumudu Transform,{\it Inter. J.
Math. Ed. Sci. Tech.,} {\bf 29(4)}, 618–-621, (1998).


\bibitem{R97}{\sl Zemanian, A. H.;}{\it Generalized Integral Transformations}, Interscience Publishers, New York (1968), Republished by Dover Publications, Inc., New York (1987).

\bibitem{R98}{\sl Zemanian, A. H.;}{\it Distribution Theory and Transform Analysis : An Introduction to Generalized Functions with Applications},Mc-Graw Hill, New York, (1965), Republished by Dover Publication, Inc., New York (1987).
\end{thebibliography}
%\end{small}




























