%
% File: chap01.tex
% Author: Victor F. Brena-Medina
% Description: Introduction chapter where the biology goes.
%
\let\textcircled=\pgftextcircled
\chapter{List of Publications}
\label{chap:List of Publications}

\begin{footnotesize}
\begin{itemize}  
\item[{[1]}] \textsc{A. D. Godase,} Recurrent formulas of the generalized Fibonacci sequences of fifth order, {\it International Journal of Mathematical Archive,} {\bf 4(6)},  61--67, (2013).

\item[{[2]}]\textsc{A. D. Godase}, Fundamental properties of multiplicative coupled Fibonacci sequences of fourth order under two specific schemes, {\it International Journal of Mathematical Archive,} {\bf 4(6)}, 74--81,(2013).

\item[{[3]}] \textsc{A. D. Godase and M. B. Dhakne,} On the properties of $k$-Fibonacci and $k$-Lucas numbers, {\it International Journal of Advances in Applied Mathematics and Mechanics,} {\bf 2(1)}, 100--106, (2014).
  
\item[{[4]}] \textsc{A. D. Godase and M. B. Dhakne,} On the properties of generalized Fibonacci like polynomials, {\it International Journal of Advances in Applied Mathematics and Mechanics,} {\bf 2(3)},234--251, (2015).

\item[{[5]}] \textsc{A. D. Godase and M. B. Dhakne,} On The Properties of Generalized Multiplicative Coupled Fibonacci Sequence of $r^{th}$ order, {\it International Journal of Advances in Applied Mathematics and Mechanics,} {\bf 2(3)}, 252--257, (2015).

\item[{[6]}]\textsc{A. D. Godase}, Summation identities for $k$-Fibonacci and $k$-Lucas numbers using matrix methods, {\it International Journal of Mathematics and Scientific Computing,} {\bf 5(2) }, 74--80, (2015).

\item[{[7]}] \textsc{A. D. Godase and M. B. Dhakne,} Determinantal Identities for $k$-Lucas Sequence, {\it Journal of New Theory,} {\bf 12}, 01--07, (2016).

\item[{[8]}] \textsc{A. D. Godase and M. B. Dhakne,} $k$-Fibonacci and $k$-Lucas Sequences as Series of Fractions, {\it Mathematical Journal of Interdisciplinary Sciences,} {\bf 4(2)}, 107--119, (2016).

\item[{[9]}]\textsc{A. D. Godase}, Properties of $k$-Fibonacci Sequence Using Matrix Method, {\it MAYFEB Journal of Mathematics,} {\bf 17},11--20, (2017).

\item[{[10]}] \textsc{A. D. Godase and M. B. Dhakne,} Some Telescoping Series for k Fibonacci and k Lucas Sequences, {\it Mathematics Today,} {\bf Submitted}, (2017).

\item[{[11]}] \textsc{A. D. Godase and M. B. Dhakne,} {Identities of Multiplicative Coupled Fibonacci Sequences of $r^{th}$ order,}{\it Journal of New Theory,} {\bf 15}, 48--60, (2017).

\item[{[12]}]\textsc{A. D. Godase and M. B. Dhakne}, Vector Approach to a New Generalization of Fibonacci Polynomial,  {\it Journal of New Theory,} {\bf 17}, 45--56,(2017).

\item[{[13]}] \textsc{A. D. Godase and M. B. Dhakne,} A Matrix Representation of a Generalized Fibonacci Polynomial, {\it Journal of New Theory,} {\bf 19}, 1--19, (2018).
 
 \item[{[14]}] \textsc{A. D. Godase,} Identities Involving $k$-Fibonacci and $k$-Lucas Sequences, {\it Mathematics Today,} {\bf 34}, 125--143, (2018). 
 
 \item[{[15]}] \textsc{A. D. Godase,} Properties of $k$-Fibonacci and $k$-Lucas Octonions, {\it Indian Journal of Pure and Applied Mathematics,} {\bf 50(4)}, 000--000, (2019).
  
\item[{[16]}] \textsc{A. D. Godase,} Hyperbolic $k$-Fibonacci and $k$-Lucas Octonions, {\it Thai Journal of  Mathematics,} {\textbf{Submitted}},  (2018). 
 
\item[{[17]}] \textsc{A. D. Godase,} Hyperbolic $k$-Fibonacci and $k$-Lucas quaternions, {\it Journal of   informatics and Mathematical Sciences,} {\textbf{Accepted}},  (2019). 
  \end{itemize}
  \end{footnotesize}